A full approximation scheme multilevel method \\ for nonlinear variational inequalities

### 2024-01-10 paper/fascd.tex
measured convergence rate for Example 8.1

FIXME RATE  The ball problem has a known exact solution $u\in W^{2,\infty}(\Omega)$ \cite{Bueler2021,Tai2003}.  Our measured convergence rate is $\|u^\star-u^J\|_{H^1(\Omega)}=O(h^{1.xx})$; compare $O(h^1)$ from theory \cite[section 5.1]{Ciarlet2002}.

>>>>

The ball problem has a known exact solution $u\in W^{2,\infty}(\Omega)$ \cite{Bueler2021,Tai2003}.  The measured convergence rate is $\|u^\star-u^J\|_{H^1(\Omega)}=O(h^{1.51})$, somewhat better than $O(h^1)$ provable from theory \cite[section 5.1]{Ciarlet2002}.
